\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
3D case minor updates / description

\blue{(a) Little intro of the case; }\\
The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions as these are decribed by figure \ref{fig:3DChannel_PermMesh}.

\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called
viscous fingers. The geometrical evolution of these patterns provides good indications about the evolution of the penetration into a zone with a less viscous fluid.

\blue{(c) then briefly describe what are the strategies to tackle these issues; }\\
Capturing and tracking the evolution of fluid patterns is important for the understanding the penetration process.

@@

\blue{(e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
While the saturation levels for phase $1$, as this is progress over time, remain between the values of $0.25-0.75$ there the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow. A comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary. Along with the individual steps as the also shown in figures \ref{fig:3DChannel_sat}(a)-(f), the evolution of the saturation front becomes more obvious. Based on the boundary conditions that implemented in this domain, the preferencial path of the flow can been seen. In a large scale enhanced oil-recovery operation this might have direct impact on the in-sity hydrocarbons located in lower permeability areas.

>>>>

\blue{(a) Little intro of the case; }\\
The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.

\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers. The geometrical evolution of these patterns provides good indications on capturing and tracking the fluid patterns.

@@

\blue{(e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
While the saturation levels for phase $1$, remain between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can been seen by the darcy velocity contours.  Initially most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region. At this point a comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary. As the flow progress, in a $2D$ domain a finger formation will start to appear. This is triggerded initially cause of the permeability differences in the domain. In a $3D$ domain though, the same finger fomration does not look the same, as it is more a description of the preferential flow path that includes smaller fingers that will break out of the flow path. Two characteristic time steps are shown in figures \ref{fig:3DChannel_sat}(a)-(f), along with the evolution of the saturation front that now becomes more obvious. Based on the boundary conditions that implemented in this domain, the preferencial path of the flow can been seen. In a large scale enhanced oil-recovery operation this might have direct impact on the in-sity hydrocarbons located in lower permeability areas.
